Handovers - SIPHER 7 Equivalent Income

### 2023-08-10 minos/validation/handovers_S7.Rmd
Tweaks to validation scripts for S7

@@

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, S7_housing_quality)
base.s <- base.dat %>%
  select(pidp, age, time, S7_housing_quality)

spaghetti_plot(spag, 'S7_housing_quality',
               save = shall.we.save,
               save.path = save.path)

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, S7_neighbourhood_safety)
base.s <- base.dat %>%
  select(pidp, age, time, S7_neighbourhood_safety)

spaghetti_plot(spag, 'S7_neighbourhood_safety',
               save = shall.we.save,
               save.path = save.path)

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, S7_physical_health)
base.s <- base.dat %>%
  select(pidp, age, time, S7_physical_health)

spaghetti_plot(spag, 'S7_physical_health',
               save = shall.we.save,
               save.path = save.path)

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, S7_mental_health)
base.s <- base.dat %>%
  select(pidp, age, time, S7_mental_health)

spaghetti_plot(spag, 'S7_mental_health',
               save = shall.we.save,
               save.path = save.path)

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, loneliness)
base.s <- base.dat %>%
  select(pidp, age, time, loneliness)

spaghetti_plot(spag, 'loneliness',
               save = shall.we.save,
               save.path = save.path)

@@

```{r}
raw.s <- raw.parity %>%
  select(pidp, age, time, nkids_ind)
base.s <- base.parity %>%
  select(pidp, age, time, nkids_ind)

spaghetti_plot(spag, 'nkids_ind',
               save = shall.we.save,
               save.path = save.path)

>>>>

### Boxplots

```{r}
handover_boxplots(raw.dat, base.dat, 'hh_income')
```

@@

### Boxplots

```{r}
handover_boxplots(raw.dat, base.dat, 'equivalent_income')
```

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, S7_housing_quality)
# base.s <- base.dat %>%
#   select(pidp, age, time, S7_housing_quality)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'S7_housing_quality',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, S7_neighbourhood_safety)
# base.s <- base.dat %>%
#   select(pidp, age, time, S7_neighbourhood_safety)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'S7_neighbourhood_safety',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, S7_physical_health)
# base.s <- base.dat %>%
#   select(pidp, age, time, S7_physical_health)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'S7_physical_health',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, S7_mental_health)
# base.s <- base.dat %>%
#   select(pidp, age, time, S7_mental_health)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'S7_mental_health',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, loneliness)
# base.s <- base.dat %>%
#   select(pidp, age, time, loneliness)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'loneliness',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

@@

```{r}
# raw.s <- raw.parity %>%
#   select(pidp, age, time, nkids_ind)
# base.s <- base.parity %>%
#   select(pidp, age, time, nkids_ind)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'nkids_ind',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```
